%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-3pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        % NAME
        {\Huge\scshape Adolfo Sanpedro Gante} 
        % SUBHEADING
        \\ US Citizen \\
        \small
        % EMAIL
        \href{mailto:adolfogante@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{adolfogante@gmail.com}} ~
        % MOBILE
        \href{tel:+17604984391}{\raisebox{-0.2\height}\faMobile\  \underline{+1-760-498-4391}} ~ 
        % LINKEDIN
        \href{https://www.linkedin.com/in/adolfogante/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/adolfogante}}  ~
        % GITHUB
        \href{https://github.com/adoante}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/adoante}} ~
        % WEBSITE
        \href{https://adolfogante.com/}{\underline{adolfogante.com}}
    \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Technical Skills  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}

    \vspace{-7pt}
    \begin{itemize}
    [leftmargin=0.15in, label={}]\small{\item{
        % LANGUAGES
        \textbf{Languages}{: C $|$ C++  $|$ Java $|$ Python  $|$ HTML/CSS  $|$ JavaScript $|$ React $|$  $|$ C\#} \\
        % TOOLS
        \textbf{Developer Tools}{: Git/GitHub $|$ VSCode $|$ Visual Studio $|$ Terminal $|$ Unity $|$ Figma} \\
        % TECHNOLOGIES
        \textbf{Technologies}{: Raspberry Pi  $|$ FDM 3D Printer Ender-3  $|$  Ultimaker Cura} \\
        }}
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
  
    % MAIN INFORMATION
    \resumeSubheading
    {California State University San Marcos}{San Marcos, CA}
    {Bachelors of Science in Computer Science, 3.7 GPA}{2023 - Anticipated Graduation June 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Selected Coursework}: Data Structures, Algorithms, Linear Algebra, Networking, Software Engineering}
        \resumeItem{\textbf{Awards}: Dean's List Fall 2023}
      \resumeItemListEnd
    \resumeSubheading
    {Palomar College}{San Marcos, CA}
    {Associates of Science in Computer Science}{Graduated 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Selected Coursework}: Linux Fundamentals, Assembly Language, Calculus}
        \resumeItem{\textbf{Awards}: Dean's List Spring 2021, Dean's List Fall 2021}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
    \resumeSubHeadingListStart
        % COMPANY 2
        \resumeSubheading
        {Watering Hope}{San Diego, CA}
            % POSITION 2
            {Web Developer Intern}{Summer 2024}
            \resumeItemListStart
                \resumeItem{Developed responsive web pages using \textbf{HTML}, \textbf{CSS}, and \textbf{JavaScript}.}
                \resumeItem{Designed and translated \textbf{Figma} mockups into functional and aesthetically pleasing web interfaces.}
                \resumeItem{Implemented interactive elements and animations with \textbf{JavaScript}, enhancing user engagement and experience.}
                \resumeItem{Maintained and updated the front-end codebase using \textbf{Git} and \textbf{GitHub} version control utilities.}
            \resumeItemListEnd

        % COMPANY 1
        \resumeSubheading
        {Island's Restaurant}{Vista, CA}
            % POSITION 1
            {Line Cook}{2022 - Present}
            \resumeItemListStart
                \resumeItem{Managed a line of five cooks, delegating tasks, coordinating rest periods and meal breaks.}
                \resumeItem{Promoted from dishwasher to Line Cook after 3 months.}
                \resumeItem{Stationed at Fry, Salad, Grill and acting Lead cook.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects} 
    \resumeSubHeadingListStart
        % Project 4
        \resumeProjectHeading
        {Math Arcade - Game Development}
        % Date
        {Spring 2024}
        \resumeItemListStart
            \resumeItem{Developed an algebra-based educational game in \textbf{Unity} using \textbf{C\#}.}
            \resumeItem{Integrated Unity Authentication and Cloud Save for user data management.}
            \resumeItem{Created and implemented 4 game modes to enhance learning.}
            \resumeItem{Designed and incorporated teaching resources within the game.}
        \resumeItemListEnd

        % Project 3
        \resumeProjectHeading
        {Banking System - Network Programming}
        % Date
        {Spring 2024}
        \resumeItemListStart
            \resumeItem{Developed a simplified banking system using \textbf{Python} Sockets over \textbf{UDP}.}
            \resumeItem{Enabled secure communication between server and client with \textbf{Python Pickle}.}
            \resumeItem{Implemented client functionalities for login, transaction processing, and transaction viewing.}
            \resumeItem{Designed server capabilities for client authentication, transaction approval/rejection, and handling multiple clients.}
        \resumeItemListEnd

        % Project 2
        \resumeProjectHeading
        {catpictures.xyz - Web Development}
        % Date
        {Fall 2023}
        \resumeItemListStart
            \resumeItem{Utilized multiple \textbf{API}s to load responsive content on the site.}
            \resumeItem{Built the site using \textbf{React} Framework, \textbf{HTML/CSS}, and \textbf{JavaScript/JSX}.}
            \resumeItem{Integrated TheCatAPI to fetch random cat images.}
            \resumeItem{Used the Advice Slip JSON API to retrieve random advice slips for image captions.}
        \resumeItemListEnd

        % Project 1
        \resumeProjectHeading
        {3x3 Macropad - Embedded Systems}
        % Date
        {Summer 2023}
        \resumeItemListStart
            \resumeItem{Utilized a \textbf{Raspberry Pi Pico Mircocontroller} to drive the program.}
            \resumeItem{Programmed in \textbf{Circuit-Python} for low-level hardware control.}
            \resumeItem{Employed an \textbf{FDM 3D printer} to create a two-piece case for the Raspberry Pi Pico and key switches.}
            \resumeItem{Hand-soldered the Raspberry Pi Pico to the key switches.}
        \resumeItemListEnd
        
    \resumeSubHeadingListEnd
 
\end{document}
